---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# inflames 🔥

The `inflames` package helps you quickly load and transform data from the Queimadas Database (INPE) into a user-friendly SF object. It leverages the power of `data.table` and `sf` for efficient data manipulation and spatial data handling.

> **Note**: This is a **hobby project**

## Installation

You can install the development version of inflames from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("M3nin0/inflames")
```

## Example

The primary function you'll be using in the `inflames` package is `inflames_read`. This function reads data from a specified CSV file from the Queimadas database and converts it into an SF object. Here's a basic example of how to use it:

```{r example, eval=FALSE}
library(inflames)

sf_object <- inflames_read('path/to/queimadas/csv/data')
```
